New_Data_Coherence

### 2019-09-24 Analysis/Coherence_Calculations_New.Rmd
new p-vals

>>>>

#Filter out extra p-values

coherence_disease = coherence_disease %>% mutate(`Biogrid P-value` = ifelse(is.na(`Biogrid Coherence`), NA, `Biogrid P-value` ))  %>% mutate(`String P-value` = ifelse(is.na(`String Coherence`), NA, `String P-value` ))  %>% mutate(`String Filt P-value` = ifelse(is.na(`String Filt Coherence`), NA, `String Filt P-value` ))
